I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-02-14 lipschitz/Lipitschz.tex
report

	\begin{abstract}
		Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formally that they are correct, with an annual competition to compare them, etc. Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN. This allows e.g. to check local robustness around an input $\vx$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $\vx$. In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs. While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern verifiers, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.

		In this paper, we analyse efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programming, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}. Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other. It is however hard to compute exactly by how much is the compensation due to the ReLU activation functions. Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy, using many queries with few 'open' ReLU nodes (for which both linear modes are considered), rather than the usual few queries with potentially many 'open' ReLU nodes. These promising results open up many different applications of the concept of compensating paths in the field of verification of DNNs.  
	\end{abstract}

>>>>

	\begin{abstract}

		Deep Neural Networks (DNNs) verification has evolved into a robust field of research, furnished with a plethora of methodologies and tools designed for formal correctness verification. This area even boasts an annual competition to benchmark these tools. Formally, the question it addresses is whether a given DNN upholds a specified property across a set of input data. For instance, it can ascertain local robustness around an input $\vx$ by verifying if the i-th output neuron consistently demonstrates the highest weight amongst all output neurons within a certain vicinity of $\vx$. In recent years, the focus has shifted towards integrating various efficient techniques—such as branch and bound, multi-neuron encoding, and MILP encoding—to optimize the balance between speed and accuracy. Although modern verifiers can efficiently validate relatively large DNNs (with tens of thousands of neurons), the challenge persists, especially when dealing with certain DNNs, even smaller ReLU DNNs comprising hundreds of neurons, thereby highlighting the ongoing need for innovative methodologies.

		In this paper, we analyse efficient algorithms  for verifying ReLU DNNs, examining abstractions like DeepPoly, Linear Programming, PRIMA, and various versions of Crown. We identify the primary cause of accuracy loss: {\em compensations}. Compensations occur when dual paths exist between a neuron pair, with one path carrying positive weights and the other negative, leading to a partial offset. However, accurately quantifying this offset is complex due to the ReLU activation functions. Leveraging this insight, we introduce a novel approach for achieving promising speed-accuracy trade-offs. This involves conducting numerous queries with a limited number of 'open' ReLU nodes (considering both linear modes) rather than the traditional approach of fewer queries with potentially many 'open' ReLU nodes. These findings not only present practical implications but also pave the way for various applications of the concept of compensating paths in the realm of DNN verification.

	\end{abstract}
